\Title

### 2019-12-13 manuscript/manuscript.tex
Add more structure to manuscript

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

\section{Source layouts}

Describe the proposed source layouts.

@@

\section{Comparison of source layouts}

Describe forward model made out of prisms, ground and airborne survey (plus noise), the
target grid, how do we score each interpolation.
Describe the Harmonica implementation of the EQL.

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

\section{Source distributions}

Describe the proposed source distributions as combination of layouts and depths
strategies.

\begin{table*}
    \begin{minipage}{80mm}
        \caption{
            Source distributions as combinations of source layouts and depth
            strategies.
        }
        \label{tab:source-distributions}
        \begin{tabular}{lccc}
            & Source bellow data & Block-reduced data & Grid sources \\ \hline
            Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
            Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        \end{tabular}
    \end{minipage}
\end{table*}

@@

\section{Comparison of source distributions}

\subsection{Synthetic Model}

Describe forward model made out of prisms.
Show prisms model?

\subsection{Synthetic Surveys}

Describe the ground and airborne survey (plus noise).
Show survey values.

\subsection{Comparisons}

Describe the target grid. Show target grid figure.
Describe the parameters used for each source distribution, how do we score each interpolation.
Describe the Harmonica implementation of the EQL.
